---
title: "Q1"
author: "Zhen Zhang"
date: "4/20/2020"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(car)
auto = read.csv("../data/Auto.csv", na.strings="?")
auto$origin = factor(auto$origin, 1:3, c("US", "Europe", "Japan"))
names(auto)
head(auto)
```
# (a) Regress mpg on cylinders, displacement, weight, and year. Comment on the signs of the estimated coefficients and note which are significantly different from 0. What is value of R2?
```{r}
fit = lm(mpg ~ cylinders + displacement + weight + year, auto)
summary(fit)
```
P(weight) and P(year) < .05,  so weight and year are significantly different from 0. And Multiple R-squared:  0.8091.

# (b) Compute the variance inflation factors. What do they tell you?
```{r}
vif(fit)
```
Only year shows no multicollinearity.

# (c) Drop weight from the model. What happens to the parameter estimates and R2?
```{r}
fit2 = lm(mpg ~ cylinders + displacement + year, auto)
summary(fit2)
```
Displacement becomes significant. And R square is decreased.

# (d) Drop weight and displacement from the model. What happens to the parameter estimates and R2?
```{r}
fit3 = lm(mpg ~ cylinders + year, auto)
summary(fit3)
```
Cylinders becomes significant. And R square is decreased.