---
title: "Q11"
author: "Zhen Zhang"
date: "4/25/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
mrcontract = expand.grid(agency=LETTERS[1:4], sup=c("local","travel"), scope=c("in-house", "subcontract"), fee=c("high","med","low"))
mrcontract$quality=c(124.3,120.6,120.7,122.6,112.7,110.2,113.5,108.6,115.1, 119.9,115.4,117.3,88.2,96,96.4,90.1,119.3,118.9,125.3,121.4,113.6,109.1,108.9, 112.3,117.2,114.4,113.4,120,92.7,91.1,90.7,87.9,90.9,95.3,88.8,92,78.6,80.6, 83.5,77.1,89.9,83,86.5,82.7,58.6,63.5,59.8,62.3)
head(mrcontract)
names(mrcontract)
```

# (a) Regress quality on agency, fee and an interaction between sup and scope. State the estimated regression equation and use drop1 to test which terms are significant.
```{r}
fit = lm(quality ~ as.factor(agency) + as.factor(fee) + as.factor(sup) : as.factor(scope), mrcontract)
drop1(fit, test = "F")
summary(fit)
```

# (b) Are there differences in quality between the agencies? To receive full credit state the null and alternative hypotheses, find the P value, state you decision (reject or not), and summarize your conclusion.
0.908 0.889 0.600 > .05, cannot reject.

# (c) Are there differences in quality between the fee values? To receive full credit state the null and alternative hypotheses, find the P value, state you decision (reject or not), and summarize your conclusion.
feemed: P-value(0.306) > .05,
feelow: P-value <2e-16, reject.

# (d) What does the coefficient for feemed tell you? Test whether it is different from 0 and discuss what the results of this tell you from a managerial perspective.
-0.9625, 0.306 > .05, cannot reject.

# (e) Is the interaction between sup and scope significant? To receive full credit state the null and alternative hypotheses, find the P value, and state you decision (reject or not).
P-value < 2e-16, reject.

# (f) Construct and interaction plot for sup and scope. Write one sentence summarizing what the interaction plot tells you.
```{r}
interaction.plot(mrcontract$sup, mrcontract$scope, mrcontract$quality, col = 1:2)
interaction.plot(mrcontract$scope, mrcontract$sup, mrcontract$quality, col = 1:2)
```
non-parallel
