---
title: "Q3"
author: "Zhen Zhang"
date: "4/24/2020"
output: 
  pdf_document: 
    latex_engine: lualatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
set.seed(1)
x1 = runif(100)
x2 = 0.5 * x1 + rnorm(100) / 10
y = 2 + 2 * x1 + 0.3 * x2 + rnorm(100)
```
# (a) Write out the form of the linear model. What are the regression coefficients?
\beta B0 = \beta B1 = 2, \beta B2 = 0.3, \sigma s = 1,
y = 2 + 2x1 + 0.3x2 + e.

# (b) What is the correlation between x1 and x2? Create a scatterplot displaying the relationship between the variables.
```{r}
cor(x1, x2)
plot(x1 ~ x2)
```

```{r}
fit = lm(y ~ x1 + x2)
summary(fit)
```
# (d) Now fit a least squares regression to predict y using only x1. Comment on your results. Can you reject the null hypothesis H0 :β1 =0?
```{r}
fit2 = lm(y ~ x1)
summary(fit2)
```

# (e) Now fit a least squares regression to predict y using only x2. Comment on your results. Can you reject the null hypothesis H0 :β1 =0?
```{r}
fit3 = lm(y ~ x2)
summary(fit3)
```
# (f) Do the results obtained in (c)–(e) contradict each other? Explain your answer.
x1 and x2 are multicollinearity.