---
title: "Q5"
author: "Zhen Zhang"
date: "4/24/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(car)
setwd("../data/")
commericial = read.table("commercial.txt", header=T)
names(commericial)
head(commericial)
```
# (a) Obtain the analysis of variance table that decomposes the regression sum of squares into extra sums of squares associated with X4; with X1 given X4; with X2 given X1 and X4; and with X3 given X1, X2 and X4. Hint use the lm and anova functions.
```{r}
fit = lm(y ~ x4 + x1 + x2 + x3, commericial) 
anova(fit)
```


# (b) Test whether X3 can be dropped from the regression model given that X1, X2 and X4 are retained. Use the F test statistic and level of significance of .01. State the null and alternative hypotheses, test statistic, P-value and decision.
```{r}
drop1(fit, test = "F")
```


# (c) Test whether both X2 and X3 can be dropped from the regression model given that X1 and X4 are retained; use alpha = 0.01. State the null and alternative hypotheses, test statistic, P -value and decision. Hint: use the pf function to find P values.
```{r}
fit2 = lm(y ~ x1 + x4, commericial)
summary(fit2)
"???"
```
# (d) Find the variance inflation factors for the full model with all four predictors in the model. What do they tell you?
```{r}
vif(fit)
```

