---
title: "Q6"
author: "Zhen Zhang"
date: "4/25/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(car)
setwd("../data/")
brand = read.table("brand.txt", header=T)
names(brand)
head(brand)
```

# (a) Find the variance inflation factors for the full model with both predictors in the model. What do they tell you?
```{r}
fit = lm(liking ~ moisture + sweetness, brand)
vif(fit)
```
pefect.

# (b) Obtain the analysis of variance table that decomposes the regression sum of squares into extra sums of squares associated with moisture; and with sweetness given moisture?
```{r}
anova(fit)
```

# (c) Obtain the analysis of variance table that decomposes the regression sum of squares into extra sums of squares associated with sweetness; and moisture given sweetness. What do you notice?
```{r}
fit2 = lm(liking ~ sweetness + moisture, brand)
anova(fit2)
```

# (d) Regress liking on moisture content only. How does the estimate of B1 in the previous part compare with the estimate in the model with both predictors?
```{r}
fit3 = lm(liking ~ moisture, brand)
coef(fit)
coef(fit3)
```

