---
title: "Q7"
author: "Zhen Zhang"
date: "4/25/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#install.packages("car") # only do this once
library(car)   # do this every R session
setwd("../data/")
quality = read.csv("quality.csv")
str(quality)
summary(quality)
```

# (a) How much variation is left unexplained by the intercept model? (this will be called the null deviance)
```{r}
deviance(lm(defect ~ 1, quality))
```

# (b) How much variation is explained by adding rate to the intercept model?
```{r}
deviance(lm(defect ~ 1, quality)) - deviance(lm(defect ~ rate, quality))
```
# (c) How much additional variation is explained by adding am to a model that already has rate in it?
```{r}
deviance(lm(defect ~ rate, quality)) - deviance(lm(defect ~ rate + am, quality))
```
# (d) How much variation is unexplained by a model having both predictors?
```{r}
deviance(lm(defect ~ rate + am, quality))
```
# (e) How much less variation is explained if we drop rate from a model with both predictors in it?
```{r}
deviance(lm(defect ~ am, quality)) - deviance(lm(defect ~ rate + am, quality))
```

# (f) Compute R2 for the two-predictor model “by hand” using only the numbers you have found above. Confirm your answer by having R compute it.
```{r}
(10929.29 - 2355.319) / 10929.29
```

# (g) Compute the F statistic for the overall test of significance by hand.
```{r}
((10929.29 - 2355.319)/2) / (2355.319/27)
```

# (h) Using the two-variable model, compute the F statistic to test H0 : B1 = 0 by hand (where B1 is for rate) (hint: it is in the drop1 output).
```{r}
5440.521/(2355.319/27)
```

